\cvsection{Volunteer Work}
\begin{cventries}
  \cventry
	{Campus Expert}
	{GitHub}
	{Remote}
	{October 2017 – Present}
	{\begin{cvitems}
		\item {India\textquotesingle{}s 2nd GitHub Campus Expert}
		\item {Manage the LNMIIT technical community and organizations with support from GitHub}
		\end{cvitems}}

  \cventry
	{Mentor of Change}
	{Atal Innovation Mission, Govt. of India}
	{Uttar Pradesh, India}
	{August 2018 – Present}
	{\begin{cvitems}
	\item {Mentor of Change Program is a strategic nation-building initiative to engage leaders who can guide and mentor students in thousands of Atal Tinkering Labs that Atal Innovation Mission has established/is in the process of establishing across India.}
	\item {I have been allotted a school in the rural areas of Ambedkar Nagar, Uttar Pradesh, India where I conduct mentoring sessions for the development of technical and entrepreneurial aspects within the underprivileged students}
		\end{cvitems}}
  \cventry
	{Co-Founder \& CTO}
	{Hackference India 2018}
	{Bengaluru, India}
	{July 2018 – Present}
	{\begin{cvitems}
		\item {Hackference India is going to the biggest open source event across India. We are organizing a deliquescent combination of Hackathon, DevRelCon and Hiring Fair, that serves to every kind of aspirations.}
		\item {I am one of the main ideators and the head community manager at Hackference India 2018}
		\item {Along with that, my work includes the handling of the technology aspects of the event}
		\end{cvitems}}
  \cventry
	{Sub Coordinator - Frontend Development}
	{Cybros - The Computer Club LNMIIT}
	{Jaipur, India}
	{August 2018 – Present}
	{\begin{cvitems}
		\item {Cybros is the main computer activity club in LNMIIT, which aims promote the coding culture within the college community}
		\item {As a Sub Coordinator in Frontend division, my aim is to organize different workshops and events within the community, aiding to the student pursuing or willing to pursue the field.}
		\end{cvitems}}
  \cventry
	{Open Source Lead}
	{Computer Society of India - LNMIIT Jaipur Chapter}
	{Jaipur, India}
	{April 2018 – Present}
	{\begin{cvitems}
		\item {Computer Society of India is a college chapter of the main CSI Foundation across India. Within this community, we aim to conduct classes and tutorials of different fields of computer science.}
		\item {As the open source lead, I manage the GitHub organization and the Semester Long Projects repositories that are undertaken by the students. Along with that, my aim is conduct workshops and regular classes on open source development, git \& GitHub facilitating the interests of students toward open source.}
		\end{cvitems}}
\end{cventries}
